CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel

### 2023-08-01 README.qmd
Add rendered result

---
format: gfm
# in future: pdf!
editor: 
  markdown: 
    wrap: sentence
---

# 10th Transport Research Arena, TRA 2024, Dublin, Ireland

**CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel**

@@

a University of Leeds, Institute for Transport Studies, Leeds, Ls2 9Jt, United Kingdom, Leeds LS2 9J, UK.

>>>>

---
format:
  gfm: default
  pdf: default
title: "CRUSE to Safe Cycling in Ireland: An Open Source Methodology to Support Active Travel"
# in future: pdf!
editor: 
  markdown: 
    wrap: sentence
---

## 10th Transport Research Arena, TRA 2024, Dublin, Ireland

@@

a University of Leeds, Institute for Transport Studies, Leeds, LS2 9JT, United Kingdom, Leeds LS2 9J, UK.
